Prison Data Analysis

### 2019-07-30 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData-LogTrans-results.Rmd
Added application on tourism data

@@

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)` ) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`) %>% 
  gather(`Base-MinT`, `Base-OLS`, key = Method, value = MSE) %>% 
  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)

>>>>

```{r}
Avg_MSE %>% 
   spread(key = `F-method`, value = MSE) %>% 
   mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
          Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_bias_Base))*100, digits = 2)) -> Avg_MSE_SS

Avg_MSE_SS %>% 
  gather(key = "F-method", value = SS_MSE, Bias_SS.MSE, Unbias_SS.MSE) %>% 
  mutate(`F-method` = recode(`F-method`, "Bias_SS.MSE" = "Bias", "Unbias_SS.MSE" = "Unbias")) %>%
  filter(`R-method` %in% c("MinT(Shrink)", "OLS", "WLS")) %>% 
  ggplot(aes(x = Forecast_Horizon, y = SS_MSE, color = `F-method`, shape = `F-method`)) + 
  facet_wrap(~ `R-method`, scales = "free_y") +
  geom_point(size = 3) + 
  scale_shape_manual(values = 15:16) +
  scale_color_manual(values = c("Red", "#33CC33")) + 
  ylab("Skill Score (MSE) %") + 
  xlab("h")

@@

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% 
  gather(`Base-OLS`, `Base-WLS`, `Base-MinT`,  key = Method, value = MSE) %>% 
  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`, scales = "free_y")
